material and methods

### 2017-08-25 man/ms_1_material_methods.Rmd
update mat and methods. Standardized anomalies

>>>>

To explore the effect of drought events on greenness we used the EVI standardized anomaly (EVI~sa)

calculated pixel-by-pixel. For each pixel we averaged all the EVI valid values within a year, and then the standardized anomaly was computed as:

$$\mathrm{EVI_{sa,\mathit{i}}}= \frac{\mathrm{EVI_{mean,\mathit{i}}-EVI_{mean,ref}}}{\sigma_{\mathrm{ref}}}$$

(anomaly divided by the standard deviation) are calculated pixel-by-pixel

The SAs, which are also referred to as normalized anomalies, are calculated by dividing the anomalies by the standard deviation. The SAs generally provide more information about the magnitude of the anomalies, because the influences of dispersion have been removed.

En el caso de las anomalías estandarizadas, utilizamos la aproximación de Gao et al. (2016) [doi:10.1038/srep26958](https://dx.doi.org/10.1038/srep26958), donde las anomalias las dividimos por la desviación estandar de los valores de EVI medio para el periodo de referencia. Las anomalías estandarizadas generalmente proporcionan mas información referente a la magnitud de la anomalía ya que las potenciales influencias de la dispersión de los datos han sido eliminadas. Por tanto las anomalías estandarizadas se calculan como: sa = (evi_year - evi_ref) / sd_ref.
